A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-16 main.tex
Updates from Overleaf

This finely calibrated, rational use of active placebo treatment, in which the physician-dispensed weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine. %啟蒙運動

@@

The new understanding is environmental signals to regulatory protein to DNA to RNA and then to protein.

@@

Some studies showed the genetic readout of some inflammatory genes in a group of people who went through a meditation process. After 8 hours of meditation, the activity of the genes changed. 

@@

Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage. These programs were acquired from other people, not from ourselves, with a survival advantage.
Being subconscious, these programs are occurring without conscious recognition and awareness. 
It affects epigenetic regulation.
Genes are not self-actualizing. The control of genes is not due to any inherent activity in the DNA itself. The change of genetic activity is due to the interaction of the cell with environmental signals.

@@

Adverse psychosocial exposures in early life, namely experiences such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased lifetime risk of adverse outcomes, including diabetes, heart disease, cancers, and psychiatric illnesses. Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}

>>>>

%This finely calibrated, rational use of active placebo treatment, in which the physician-dispensed weak, physiologically active substance in order to please and calm the patient rather than to cure the patient's underlying disorder, was a product of the rational scientific culture of the 18th century Scottish Enlightenment and its embrace of a grounded, empirical approach to medicine. %啟蒙運動

@@

The central dogma of molecular biology should be modified as environmental signals to regulatory protein to DNA to RNA and then to protein.

@@

Some studies showed that after 8 hours of meditation, the expression of some inflammatory genes changed\cite{Gustafson2017}.

@@

%Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage. These programs were acquired from other people, not from ourselves, with a survival advantage.
Being subconscious, those programs acquired from other people before age 7, are occurring without conscious recognition and awareness. 
The survival advantage programs, such as limitation, disempowerment, and self-sabotage, will affect epigenetic regulation.
Genes are not self-actualizing. 
The regulation of genetic activity is due to the interaction of the cell with environmental signals.
Genes are not self-actualizing. %The control of genes is not due to any inherent activity in the DNA itself. 
The regulation of genetic activity is due to the interaction of the cell with environmental signals.

@@

Adverse psychosocial experiences in early life, such as child maltreatment, caregiver stress, and community violence, have been associated in epidemiological studies with an increased risk of diabetes, heart disease, cancers, and psychiatric illnesses. 
The possible molecular mechanisms could be related with the mind-brain-body axis\cite{Berens2017}.
%Additional work has shed light on the potential molecular mechanisms by which early adversity becomes "biologically embedded" in altered physiology across body systems.\cite{Berens2017}
